---
title: "Lab 5"
author: "Chase Tarr"
date: "10/25/2021"
output: 
  html_document: 
    theme: spacelab
    toc: yes
    code_folding: hide # when we knit, this will allow code to be shown or hidden
---

Hitting setting gear and clicking output options allows you to change theme and insert a table of contents
```{r setup, include=TRUE, warning = FALSE, messages = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(effsize)
```

## Part 1: Confidence Intervals
  - In this section we will use the `t.test()` function to calculate confidence intervals

### Example 1
  - Create a single mock sample containing a number of values, then learnt to use `t.test()` to return confidence intervals, and learn about in-line code referencing so our text becomes more reproducible, too.
  
```{r}
# Create a mock sample
otter_lengths <- c(30, 45, 28, 31, 34, 46, 52, 29, 90, 72, 112)

# Find confidence interval from sample: 
otter_ci <- t.test(otter_lengths)

# Find the Standard Dev
otter_sd <- sd(otter_lengths)

otter_ci$statistic

```
  - Confidence interval states that when taking multiple samples from this population, we expect 95% of confidence intervals to be within the mean interval 29.08-44.67

  - Mean otter length is 36.9 inches $\pm$ 9.3 (mean $\pm$ sd, n = 8) with a 95% confidence interval of [29.1, 44.7] inches. (NEED TO ADD SAMPLE SIZE, n) (ALSO NEED TO ADD SD described with the mean plus or minus the sd as seen above in parenthesis)

learn: when calling things from list:
  
  - objectname$valuename[refer to element in bracket, 1, 2 etc)]
  ex: otter_ci$p.value 
  ex: otter_ci$conf.int

#### Now, using in-line referencing
  - Mean otter length is `r otter_ci$estimate`
  - Mean otter length is `r round(otter_ci$estimate, 1)` inches with a 95% confidence interval of [`r otter_ci$conf.int[1]`, `r otter_ci$conf.int[2]`] inches.
  - round the value using `r round(otter_ci$conf.int[2],1)`

## Part 2: Two-Sample t-tests

#### Example 1

  - Make two mock samples, and ask the question: do we have sufficient evidence to make us reject the null hypothesis that these samples were drawn from populations with the  same mean?
  
```{r}
# Make my mock samples
oak_trees <- c(20, 19, 24, 28, 34, 12, 14, 25)

pine_trees <- c(39, 26, 20, 30, 37, 22, 19, 18)

# Two sample t-test
trees_t <- t.test(oak_trees, pine_trees)

# Null Hypothesis is that our mean heights are the same
  # or... Trees are drawn from populations with the same mean height

```


The mean heights of o;ak and pine trees were (X +- Y), and  (X +- Y), respectively, and the difference was not significant (t (`r trees_t$parameter`) = `r trees_t$statistic`, p = `r trees_t$p.value` )












